---
title: "NBA-Basketball-analysis"
author: "Jesus Gonzalez Ferrer"
date: "10/3/2021"
output: html_document
---
```{r}
setwd("C:/Users/jesus/proyectos/JGF_R_projects/tidytuesday/Basketball_reference_project")
library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_light())
```



```{r}
NBA_df <- read.csv("NBA.csv")
```

```{r}
temp_21 <- NBA_df %>% 
  filter(Season == "2020-21")
```

```{r}
temp_21 %>%
  filter(MP >= 300, G >= 20, PTS >= 20) %>% 
  ggplot(aes(x = DRtg, y = ORtg)) +
  geom_point() +
  geom_text(aes(label = Player))
```

```{r}
temp_21 %>%
  filter(MP >= 300, G >= 20) %>%
  top_n(n = 70, PTS) %>% 
  ggplot(aes(x = ORtg, y = DRtg)) +
  geom_point() +
  geom_text(aes(label = Player)) +
  geom_smooth(method=lm, se = FALSE)
```
It is better the greater the ORtg and the lower the DRtg

```{r}
temp_21 %>%
  filter(MP >= 300, G >= 20) %>%
  top_n(n = 70, PTS) %>% 
  ggplot(aes(x = PTS, y = FG.)) +
  geom_point() +
  geom_text(aes(label = Player)) +
  geom_smooth(method=lm, se = FALSE)
```
Here we can see a bias towards big man or people who attack close to the rim. 
This happens because the stat we are taking into account
is FG percentage and not the adjusted FG that takes into account that a 3 is 
worth more than a 2 point shot. We should get the effective FG percentage
```{r}
temp_21 %>%
  mutate(eFG = (FG + 0.5*X3P)/FGA) %>% 
  filter(MP >= 300, G >= 20) %>%
  top_n(n = 70, PTS) %>% 
  ggplot(aes(x = PTS, y = eFG)) +
  geom_point() +
  geom_text(aes(label = Player)) +
  geom_smooth(method=lm, se = FALSE)
```

Here we can see the real difference. For example, if we look at curry in the two
graphs we can see how this adjustment better reflects the reality of the game.


